\documentclass[german,headsepline]{scrartcl}
\usepackage{beamerarticle}
\usepackage{hyperref}
\hypersetup{
		unicode=true,
		pdfusetitle,
		bookmarks=true,
		bookmarksnumbered=false,
		bookmarksopen=false,
		breaklinks=false,
		backref=false,
		% pdfborder={0 0 0},
    pdfborderstyle={/S/U/W 0.2}, % underline links instead of boxes
    linkbordercolor=red,       % color of internal links
    citebordercolor=green,     % color of links to bibliography
    filebordercolor=magenta,   % color of file links
    urlbordercolor=blue        % color of external links
}
\usepackage{geometry}
\geometry{verbose,tmargin=2mm,bmargin=78mm,lmargin=32mm,rmargin=32mm}
\setcounter{secnumdepth}{0}
\setlength{\parskip}{\bigskipamount}
\setlength{\parindent}{0pt}
\usepackage{graphics}
\usepackage{setspace}
\usepackage{multicol}
\usepackage[manualmark,headsepline]{scrpage2}
\headheight4cm
\pagestyle{scrheadings}
\addtokomafont{sectioning}{\rmfamily} %auch Ueberschriften in Serifenschrift
\addtokomafont{descriptionlabel}{\rmfamily}
\usepackage{textcomp}

\let\stdsection\section
\renewcommand\section{\newpage\stdsection}

\makeatother
\makeatletter
\lohead{\@title}
\ohead{\@author, \@date}
\setjobnamebeamerversion{beamer}
\usepackage[utf8x]{inputenc}
\usepackage[german]{babel}
\usepackage{float}
\usepackage{courier}
\usepackage{multicol}
\usepackage{listings}
\lstset{inputencoding=utf8x, breaklines=true, basicstyle=\footnotesize\ttfamily}
\lstset{literate=%
{Ö}{{\"O}}1
{Ä}{{\"A}}1
{Ü}{{\"U}}1
{ß}{{\ss}}2
{ä}{{\"a}}1
{ö}{{\"o}}1
{ü}{{\"u}}1
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Literatur und Links}
\author{Sven Koesling}
\institute{ETH--Bibliothek}
\date{Herbst 2017}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
{\renewcommand\labelitemi{}
\subsection{Literatur}
\begin{itemize}
  \item Gumm, Heinz-Peter, Sommer, Manfred, and Hesse, Wolfgang:\\
    \href{http://www.library.ethz.ch/DADS:default_scope:ebi01_prod007595267}{\it Einführung in die Informatik}\\
    10., Vollst. überarb. Aufl. ed. München: Oldenbourg, 2013. Print.
  \item Redmond, Eric, and Wilson, Jim:\\
    \href{http://www.library.ethz.ch/DADS:default_scope:ebi01_prod006803093}{\it Seven Databases in Seven Weeks : A Guide to Modern Databases and the NoSQL Movement}\\
    Dallas, Texas: Pragmatic Bookshelf, 2012. Print. The Pragmatic Programmers.
  \item Tate, Bruce:\\
    \href{http://www.library.ethz.ch/DADS:default_scope:ebi01_prod006317724}{\it Seven Languages in Seven Weeks : A Pragmatic Guide to Learning Programming Languages}\\
    Dallas: Pragmatic Bookshelf, 2011. Print.
  \item Abdelhamid, Rames:\\
    \href{http://www.library.ethz.ch/DADS:default_scope:ebi01_prod001553956}{\it Das Vieweg-LATEX2e-Buch : Eine Praxisorientierte Einführung}\\
    3., Vollst. überarb. Und Erw. Aufl. ed. Braunschweig [etc.: Vieweg, 1996. Print. Studium Und Ausbildung.
  \item Wüst, Karl, Gervais, Arthur:\\
    \href{https://eprint.iacr.org/2017/375.pdf}{Do you need a Blockchain?}
\end{itemize}

\subsection{Links}
\begin{itemize}
  \item \href{http://actu.epfl.ch/news/the-matterhorn-like-you-ve-never-seen-it/}{The Matterhorn like you've never seen it}
  \item \href{https://www.nmc.org/publication/nmc-horizon-report-2017-library-edition/}{Horizon Report 2017 Library Edition}
  \item \href{https://www.youtube.com/watch?v=HgmETqWeFrs}{NEBIS-Verbundtagung/Assemblée annuelle 2015: Keynote Magnus Pfeffer: Cloud Computing}
\end{itemize}

\textbf{Humoreskes}
\begin{itemize}
  \item \href{https://youtu.be/BKorP55Aqvg}{You are an expert}
  \item \href{https://youtu.be/MAYBhIiB82E}{Kickass Librarian}
\end{itemize}

\end{document}
