\section{Literatur und Links}
{\renewcommand\labelitemi{}
\subsection{Literatur}
\begin{itemize}
  \item Gumm, Heinz-Peter, Sommer, Manfred, and Hesse, Wolfgang:\\
    \href{http://www.library.ethz.ch/DADS:default_scope:ebi01_prod007595267}{\it Einführung in die Informatik}\\
    10., Vollst. überarb. Aufl. ed. München: Oldenbourg, 2013. Print.
  \item Redmond, Eric, and Wilson, Jim:\\
    \href{http://www.library.ethz.ch/DADS:default_scope:ebi01_prod006803093}{\it Seven Databases in Seven Weeks : A Guide to Modern Databases and the NoSQL Movement}\\
    Dallas, Texas: Pragmatic Bookshelf, 2012. Print. The Pragmatic Programmers.
  \item Tate, Bruce:\\
    \href{http://www.library.ethz.ch/DADS:default_scope:ebi01_prod006317724}{\it Seven Languages in Seven Weeks : A Pragmatic Guide to Learning Programming Languages}\\
    Dallas: Pragmatic Bookshelf, 2011. Print.
  \item Abdelhamid, Rames:\\
    \href{http://www.library.ethz.ch/DADS:default_scope:ebi01_prod001553956}{\it Das Vieweg-LATEX2e-Buch : Eine Praxisorientierte Einführung}\\
    3., Vollst. überarb. Und Erw. Aufl. ed. Braunschweig [etc.: Vieweg, 1996. Print. Studium Und Ausbildung.
  \item Wüst, Karl, Gervais, Arthur:\\
    \href{https://eprint.iacr.org/2017/375.pdf}{Do you need a Blockchain?}
\end{itemize}

\subsection{Links}
\begin{itemize}
  \item \href{http://actu.epfl.ch/news/the-matterhorn-like-you-ve-never-seen-it/}{The Matterhorn like you've never seen it}
  \item \href{https://www.nmc.org/publication/nmc-horizon-report-2017-library-edition/}{Horizon Report 2017 Library Edition}
  \item \href{https://www.youtube.com/watch?v=HgmETqWeFrs}{NEBIS-Verbundtagung/Assemblée annuelle 2015: Keynote Magnus Pfeffer: Cloud Computing}
  \item \href{https://www.ethz.ch/de/news-und-veranstaltungen/eth-news/news/2017/09/data-science-interview-roger-wattenhofer.html}{Blockchain ist ein Hype}
\end{itemize}

\subsubsection{Humoreskes}
\begin{itemize}
  \item \href{https://youtu.be/BKorP55Aqvg}{You are an expert}
  \item \href{https://youtu.be/MAYBhIiB82E}{Kickass Librarian}
\end{itemize}

